Topic modeling on EU and the USA research projects

### 2017-06-28 thesis_report/draft_thesis.tex
Minor fixes in 5.4 & 5.5

In figure \ref{totaltopicsEU} we show the 10 topics described by
the 20 top words with the highest probability of belonging
to the topic. The size of each word is in proportion to each
probability; the bigger the word, the higher the probability. Each
wordcloud describes a topic, which we can find intuitively. 
We ran the LDA model with 7000
iterations and the same value of the rest of the
parameters, as described in section \ref{modelinference}. Below are
listed the topics that we found corresponding to the words that
describe them:
\begin{itemize}
\item[] Topic 0: Molecular biology
\item[] Topic 1: Materials \& Manufacturing
\item[] Topic 2: Social policy
\item[] Topic 3: Disease detection \& treatment
\item[] Topic 4: Materials science / Physics
\item[] Topic 5: Transport \& Energy
\item[] Topic 6: Business \& Innovation
\item[] Topic 7: Climate change / Environment
\item[] Topic 8: Molecular mechanisms
\item[] Topic 9: Information systems
\item[] Topic 10: International research
\item[] Topic 11: Energy production
\end{itemize}
\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic0_all.png}} &
\subfloat[Materials \& Manufacturing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic1_all.png}} &
\subfloat[Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic2_all.png}}\\
\subfloat[Disease detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic3_all.png}} &
\subfloat[Materials science / Physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic4_all.png}} &
\subfloat[Transport \& Energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic5_all.png}}\\
\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic6_all.png}} &
\subfloat[Climate change / Environment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic7_all.png}} &
\subfloat[Molecular mechanisms]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic8_all.png}}\\
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic9_all.png}} &
\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic10_all.png}} &
\subfloat[Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic11_all.png}}\\
\end{tabular}
\caption{Wordclouds of topics of the EU dataset (1994-2017)}
\label{totaltopicsEU}
\end{figure}
\end{center}

@@

Each one of the wordclouds in figure \ref{usatotal} represents a topic.
The topics that are described in the wordclouds are listed below:

>>>>

In figure \ref{totaltopicsEU} we show the 10 topics described by
the 20 top words with the highest probability of belonging
to the topic. The size of each word is in proportion to each
probability; the bigger the word, the higher the probability. Each
wordcloud describes a topic, which we can find intuitively. 
We ran the LDA model with 7000
iterations and the same value of the rest of the
parameters, as described in section \ref{modelinference}. We assigned titles 
to the topics, based on the words that describe them. Below are
listed the titles of topics:
\begin{itemize}
\item[] Topic 0: Molecular biology
\item[] Topic 1: Materials \& Manufacturing
\item[] Topic 2: Social policy
\item[] Topic 3: Disease detection \& treatment
\item[] Topic 4: Materials science / Physics
\item[] Topic 5: Transport \& Energy
\item[] Topic 6: Business \& Innovation
\item[] Topic 7: Climate change / Environment
\item[] Topic 8: Molecular mechanisms
\item[] Topic 9: Information systems
\item[] Topic 10: International research
\item[] Topic 11: Energy production
\end{itemize}
\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic0_all.png}} &
\subfloat[Materials \& Manufacturing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic1_all.png}} &
\subfloat[Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic2_all.png}}\\
\subfloat[Disease detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic3_all.png}} &
\subfloat[Materials science / Physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic4_all.png}} &
\subfloat[Transport \& Energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic5_all.png}}\\
\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic6_all.png}} &
\subfloat[Climate change / Environment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic7_all.png}} &
\subfloat[Molecular mechanisms]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic8_all.png}}\\
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic9_all.png}} &
\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic10_all.png}} &
\subfloat[Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic11_all.png}}\\
\end{tabular}
\caption{Wordclouds of topics of the EU dataset (1994-2017)}
\label{totaltopicsEU}
\end{figure}
\end{center}

@@

Each one of the wordclouds in figure \ref{usatotal} represents a topic.
The titles of the topics that are described in the wordclouds are listed below:
